Association of Mental Health Factors with COVID-19 Test Status

### 2025-05-02 products/manuscript/Manuscript.qmd
Part 6 final

```{r, echo=FALSE, message=FALSE}
# load a few R packages
library(here)
library(knitr)
library(tidyverse)
library(mice)
library(miceadds)
library(mitools)
library(tableone)
library(survey)
library(gt)
here()
```

@@

* Annalise Cramer$^{1,2 \land}$ (ORCID: 0009-0002-8718-3593)

@@

```{r}
#| label: fig-schematic
#| fig-cap: "Figure 1. Flowchart depicting methodology of this study."
#| echo: FALSE
knitr::include_graphics(here("results","figures", "flowchart.png"))
```

@@

```{r}
#| label: tab-1
#| fig-cap: "Table 1. Table depicting porportion of responses among all observations, incliding missingness."
#| echo: FALSE
knitr::include_graphics(here("results","figures", "summary_table_with_nas.png"))
```

@@

```{r}
#| label: tab-2
#| fig-cap: "Table 2. Table depicting prevalence estimates with 95% confidence intervals among the United State population. Results are split by COVID-19 test status, and shown for overall population."
#| echo: FALSE
knitr::include_graphics(here("results","figures", "table1_imputed.png"))
```

@@

```{r}
#| label: tbl-summarytable
#| tbl-cap: "Table 3. Assocation of mental health factors with positive COVID-19 test results among the United State population."
#| echo: FALSE
here()
knitr::include_graphics(here("results","figures", "single_model_table.png"))
```

@@

To evalaute the performance of these models, the area under the curve (AUC) was calculated. This metric was chosen due to it's discrimination between binary outcome of the COVID-19 variable. Higher AUC indicates better model preformance. Desspite the Logistic Regression model and the Lasso Regression model have the same mean AUC, they are not the same, shown by the differing values for the imputations. Code was checked to ensure the models were not the same.

```{r}
#| label: fig-aucplot
#| fig-cap: "Figure 2. Plot comparing area under the curve (AUC) metrics among imputations between logistic regression model, LASSO regression model, and random forest model. Higher AUC indicates better preformance. "
#| echo: FALSE
here()
knitr::include_graphics(here("results","figures", "auc_comparison_plot.png"))
```

@@

```{r}
#| label: fig-log-plot
#| fig-cap: "Figure 3. Logistic Regression calibration plot."
#| echo: FALSE
here()
knitr::include_graphics(here("results","figures", "log_calibration_plot.png"))
```

```{r}
#| label: fig-lasso-plot
#| fig-cap: "Figure 4. LASSO Regression calibration plot."
#| echo: FALSE
here()
knitr::include_graphics(here("results","figures", "lasso_calibration_plot.png"))
```

```{r}
#| label: fig-rf-plot
#| fig-cap: "Figure 5. Random Forest calibration plot. "
#| echo: FALSE
here()
knitr::include_graphics(here("results","figures", "rf_calibration_all_imputations.png"))
```

@@

## Conclusions
We found that indications of poor mental health were common in the population United States population, with trouble sleeping, exercise, and getting enough sleep, while depressed and social isolation occured in at a lower prevalence (Tab. 2). Sleep difficulties were commonly reported during the SARS-CoV-2 pandemic, which supports these results^$5$.

>>>>

```{r, echo=FALSE, message=FALSE}
# load a few R packages
library(here)
library(knitr)
library(tidyverse)
library(mice)
library(miceadds)
library(mitools)
library(tableone)
library(survey)
library(gt)
```

@@

* Annalise Cramer$^{1,2}$ (ORCID: 0009-0002-8718-3593)

@@

```{r}
#| label: fig-schematic
#| fig-cap: "Flowchart depicting methodology of this study."
#| echo: FALSE
knitr::include_graphics(here("results","figures", "flowchart.png"))
```

@@

```{r}
#| label: tbl-1
#| tbl-cap: "Table depicting porportion of responses among all observations, incliding missingness."
#| echo: FALSE
knitr::include_graphics(here("results","figures", "summary_table_with_nas.png"))
```

@@

```{r}
#| label: tbl-2
#| tbl-cap: "Table depicting prevalence estimates with 95% confidence intervals among the United State population. Results are split by COVID-19 test status, and shown for overall population."
#| echo: FALSE
knitr::include_graphics(here("results","figures", "table1_imputed.png"))
```

@@

```{r}
#| label: tbl-summarytable
#| tbl-cap: "Assocation of mental health factors with positive COVID-19 test results among the United State population."
#| echo: FALSE
knitr::include_graphics(here("results","figures", "single_model_table.png"))
```

@@

To evalaute the performance of these models, the area under the curve (AUC) was calculated. This metric was chosen due to it's discrimination between binary outcome of the COVID-19 variable. Higher AUC indicates better model preformance. Despite the Logistic Regression model and the Lasso Regression model have the same mean AUC, they are not the same, shown by the differing values for the imputations. Code was checked to ensure the models were not the same.

```{r}
#| label: fig-aucplot
#| fig-cap: "Plot comparing area under the curve (AUC) metrics among imputations between logistic regression model, LASSO regression model, and random forest model. Higher AUC indicates better preformance. "
#| echo: FALSE
knitr::include_graphics(here("results","figures", "auc_comparison_plot.png"))
```

@@

```{r}
#| label: fig-log-plot
#| fig-cap: "Logistic Regression calibration plot."
#| echo: FALSE
knitr::include_graphics(here("results","figures", "log_calibration_plot.png"))
```

```{r}
#| label: fig-lasso-plot
#| fig-cap: "LASSO Regression calibration plot."
#| echo: FALSE
knitr::include_graphics(here("results","figures", "lasso_calibration_plot.png"))
```

```{r}
#| label: fig-rf-plot
#| fig-cap: "Random Forest calibration plot. "
#| echo: FALSE
knitr::include_graphics(here("results","figures", "rf_calibration_all_imputations.png"))
```

@@

## Conclusions
We found that indications of poor mental health were common in the population United States population, with trouble sleeping, exercise, and getting enough sleep, while depressed and social isolation occured in at a lower prevalence (Tab. 2). Sleep difficulties were commonly reported during the SARS-CoV-2 pandemic, which supports these results$^5$.
